A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-05-07 ionic_liquids.tex
revision I

A first inspection of Fig.~\ref{fig:dihedrals_emim} reveals a similar behavior of the models of \ce{[emim]^+} due to Koller \textit{et al.} \cite{Koller_2012} and Liu \textit{et al.} \cite{Liu_2014}. This was expected as both were developed based on the AMBER force field ~\cite{Cornell_1995}. In addition, Figs.~\ref{fig:dihedrals_emim}(a) and \ref{fig:dihedrals_emim}(b) are symmetric, which means that atoms C1, N2, and C2 are coplanar. In Fig.~\ref{fig:dihedrals_emim}(a), the most likely angles can be found in a narrow region around 90$^{\circ}$ and 270$^{\circ}$. Given that these angles correspond to the same configuration in the \textit{united-atom} representation of \ce{[emim]^+}, we built all the rigid bodies specifying the value of 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1. The other models showed a larger flexibility with high probability regions that extend in a broad range of angle values. Despite this, it was possible to build more than one type of rigid body by specifying the most probables angles for C6-C5-N2-C1. In the case of Liu \textit{et al.} \cite{Liu_2014}, those angles correspond to the values of  90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed the angles of 102.6$^{\circ}$ and -102.6$^{\circ}$. For those cases, two types of rigid bodies were built in equal proportion. Fig.~\ref{fig:dihedrals_emim}(d) shows that the model of Weber and Kirchner \cite{Weber_2016} presents a non negligible probability of sampling the angle value of 0$^{\circ}$, which notably differs from what was observed for the other models. In this case, we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of the rigid bodies, respectively; and for the remaining 15~\% we specified the angle of 0$^{\circ}$.

@@

For the simulation strategies (1) and (2) we have also compared the results of relevant radial distribution functions (RDFs), which can be found in the Supplementary material. The better agreement was found for the force fields due to Koller \textit{et al.} \cite{Koller_2012} and Batista \textit{et al.} \cite{Batista_2015}. Even though the model of Liu \textit{et al.} \cite{Liu_2014} presented small deviations, the simulation with rigid bodies qualitatively reproduced the RDFs obtained for flexible ions. Although not shown here, these conclusions are valid for other calculated RDFs: N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion). The model of Weber and Kirchner \cite{Weber_2016}, 
on the other hand, presented important discrepancies in the RDFs for the pairs C5(cation)-N(anion) and C2(cation)-B(anion) when using rigid bodies. That is why in this case we have considered as being rigid only the imidazolium ring while letting  the ethyl chain flexible.

@@

A study of dihedrals was also carried out for \ce{[emim][NTf_2]}. The CDF of dihedrals C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the behaviour of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 corresponds to 0$^{\circ}$. This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}. With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.}~\cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation (Fig.~\ref{fig:kdderman_a}). Fig.~\ref{fig:cddf_anion}, which corresponds to the CDF for the contiguous dihedrals C1-S1-N1-S2 and S1-N1-S2-C2, verifies qualitatively what was observed by Deetlefs \textit{et al.} \cite{Deetlefs_2006}. Given that the flexibility of \ce{[NTf_2]^-} gives rise to highly different conformation, a more rigorous strategy for building rigid bodies would be required. Thus, for \ce{[emim][NTf_2]} we have considered flexible ions and the DSF method, which resulted in a simulated density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.

@@

  \includegraphics[width=\linewidth]{Ludwig_anion.png}%
\caption{Combined distribution function (CDF) of anion}
\label{fig:dihedrals_anion}
\end{figure}

\begin{table*}
\caption{Densities of \ce{[emim][B(CN)_4]} predicted from MD NPT simulations at 298.15 K and 1 atm. The experimental density is $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
\begin{threeparttable}
\begin{tabular}{ c  c  c  c  c}  
\hline \hline
$\text{[emim]}$[B(CN)\textsubscript{4}] & $T_{\text{sim}}$ & $ P_{\text{sim}} $ & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
model & (K) &  (atm) &  (g/cm$^{3}$) &  \\
			\hline
		 \multicolumn{5}{c}{Flexible ions/Ewald method}\\

Koller y col.~\cite{Koller_2012}  & 298.14 $\pm$  0.02 & 0 $\pm$ 2 & 1.046 & 1.0 \\
Batista y col.~\cite{Batista_2015} & 298.15 $\pm$ 0.01  & 1 $\pm$ 1 & 0.989 & 4.6  \\
Liu y col.~\cite{Liu_2014}  & 298.14 $\pm$ 0.01 & 0 $\pm$ 1 & 1.001 & 3.4  \\
Weber y Kirchner.~\cite{Weber_2016}  & 298.16  $\pm$ 0.01 & 1 $\pm$ 1 & 1.015 & 2.1  \\
	 \multicolumn{5}{c}{Rigid ions/DSF method}\\
Koller y col.~\cite{Koller_2012}   & 298.42  $\pm$ 0.03  & 1 $\pm$ 1 & 1.038 & 0.2 \\
Batista y col.~\cite{Batista_2015} & 298.43 $\pm$ 0.02  & 0.9 $\pm$ 0.7  & 0.988 & 4.7  \\
Liu y col.~\cite{Liu_2014}  & 298.46 $\pm$ 0.02 & 1.2  $\pm$ 0.8 & 0.991 &  4.4 \\
Weber y Kirchner.~\cite{Weber_2016} &  298.41 $\pm$ 0.03 & 1.1 $\pm$ 0.8 & 1.022 & 1.4  \\
 \hline \hline
\label{table:props_dsf} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$($\rho^{\text{exp}}$$ - $$\rho^{\text{sim}}$)/$\rho^{\text{exp}}$.
\end{tablenotes}
\end{threeparttable}
\end{table*}

@@

For each model of \ce{[emim][B(CN)_4]} described in Sec~\ref{sec:force_field_il}, in Table \ref{table:henry} we present the results corresponding to the solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\ref{eq:henry_eq}, which we compare with the experimental value reported by Mahurin \textit{et al.} \cite{Mahurin_2010}. Table \ref{table:henry} also includes the results for [emim][Tf\textsubscript{2}N] and the experimental $K_s$ obtained by Finotello \textit{et al.} \cite{Finotello_2008}. The uncertainties were calculated using standard error propagation.

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] at T = 298.15 K and P = 1 atm. The experimental Henry constants in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}, respectively.}
\begin{tabular}{ c c c  c  c  c  c }  
\toprule
Model & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
& (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
			\hline
			\multicolumn{4}{c}{\ce{[emim][B(CN)_4]}} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
			\hline
Koller \textit{et al.} \cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
Batista \textit{et al.} \cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
Liu \textit{et al.} \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
Weber y Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
\hline
		\multicolumn{4}{c}{[emim][Tf\textsubscript{2}N]} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
		\hline
 K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
 \bottomrule
\label{table:henry} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^{\text{sim}})/K_s^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

First, it should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.}~\cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent simulations in $\lambda_{\text{LJ}}$ and $\lambda_{\, \text{Coul}}$. Moreover, the value of $\Delta G_{\text{sim}}$ corresponding to [emim][Tf\textsubscript{2}N] is very close to -0.534 kcal/mol, which was obtained by Kerl \textit{et al.} \cite{Kerl__2017} using the FEP method \cite{Zwanzig_1954} with no uncertainty reported. These consistencies serve for validating the methodological approaches we employed in each case.

From Table \ref{table:henry} one can see that the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental value of $K_s$. If we look at the $\Delta G_{\, \text{LJ}}$ profiles in Fig.~\ref{fig:deltag} we observe that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014}, the maximum of free energy occurs at lower values of energy, suggesting that these models underestimate the interatomic interactions, which explains the ``facility'' to insert the solute molecule as well as their failure to reproduce the experimental densities.

\begin{figure}[]
\includegraphics[width=\linewidth]{free_energy_paper}
\label{fig:deltag}
\end{figure}

The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in [emim][Tf\textsubscript{2}N]. In order to have a graphical insight of solvation, we have also obtained the spatial distribution functions (SDFs) \cite{Svishchev_1993} using the software packages TRAVIS~\cite{Brehm_2011} and VMD~\cite{HUMP96}. For that, we carried out MD NPT simulations of the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] with a solute molar fraction of 0.1. In Fig.~\ref{fig:sdf_ions} we show the SDFs of the ions around a molecule of \ce{CO_2}. The isovalues were determined visually so as to observe the first solvation shell. From Fig.~\ref{fig:ludwig_sdf}(b), which correspond to the ions \ce{[emim]^+} and \ce{[NTf_2]^-}, it can be seen that the region with a low probability of finding an ion is larger than for \ce{[emim][B(CN)_4]}. In Fig.~\ref{fig:anions} we have plotted together the SDFs corresponding to the anions and we note that the first solvation shell for [B(CN)\textsubscript{4}]$^{-}$ occur at a sligthly shorter distance than for \ce{[NTf_2]^-}, in accordance with the more favorable solvation suggested by the free energy results.

@@

The task of accurately predicting $\gamma^{\, \infty}$ is more challenging given that, according to Eq.~\ref{eq:gamma_inf}, one should be able to reproduce the solvation free energies in both the pure solute and the solvent. In Table~\ref{table:mu_solutos} we present the simulated densities and the solvation free energies  $(\Delta G^{0}_{\text{sim}})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}. It should be pointed out that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ of cyclohexane. Note that only in the case of ethanol we have reproduced $\Delta G^{0}_\text{exp}$ while the relative error for the other solutes is around 10\%.

The results of $\gamma^{\, \infty}$ for the solutes in \ce{[emim][B(CN)_4]} are shown in Table~\ref{table:gamma}. For benzene and water, the predictions are very accurate, but thay are a result of error compensations given the divergences verified in Table~\ref{table:mu_solutos}. This makes necessary to review the force fields of the solutes. From Table \ref{table:gamma} one can also note that the experimental $\gamma^{\, \infty}$ for hexane at the close temperatures of 298.15 K and 303 K considerably differ. It is therefore difficult to assess the reliability of the simulated results in this case.

>>>>

A first inspection of Fig.~\ref{fig:dihedrals_emim} reveals a similar behavior of the models of \ce{[emim]^+} due to Koller \textit{et al.} \cite{Koller_2012} and Liu \textit{et al.} \cite{Liu_2014}. This was expected as both were developed based on the AMBER force field ~\cite{Cornell_1995}. In addition, Figs.~\ref{fig:dihedrals_emim}(a) and \ref{fig:dihedrals_emim}(b) are symmetric, which means that atoms C1, N2, and C2 are coplanar. In Fig.~\ref{fig:dihedrals_emim}(a), the most likely angles can be found in a narrow region around 90$^{\circ}$ and 270$^{\circ}$. Given that these angles correspond to the same configuration in the \textit{united-atom} representation of \ce{[emim]^+}, we built all the rigid bodies specifying the value of 90$^{\circ}$ for the dihedral angle of C6-C5-N2-C1. The other models showed a larger flexibility with high probability regions that extend in a broad range of angle values. Despite this, it was possible to build more than one type of rigid body by specifying the most probables angles of C6-C5-N2-C1. In the case of Liu \textit{et al.} \cite{Liu_2014}, those angles correspond to the values of  90$^{\circ}$ and -90$^{\circ}$, while for the model of Batista \textit{et al.} \cite{Batista_2015}, we employed the angles of 102.6$^{\circ}$ and -102.6$^{\circ}$. For those cases, two types of rigid bodies were built in equal proportion. Fig.~\ref{fig:dihedrals_emim}(d) shows that the model of Weber and Kirchner \cite{Weber_2016} presents a non-negligible probability of sampling the angle value of 0$^{\circ}$, which notably differs from what was observed for the other models. In this case, we defined four types of rigid bodies: 150$^{\circ}$, 180$^{\circ}$ and 210$^{\circ}$ were employed to build 30~\%, 25~\% and 30~\% of the rigid bodies, respectively; and for the remaining 15~\% we specified the angle of 0$^{\circ}$.

@@

For the simulation strategies (1) and (2) we have also compared the results of relevant radial distribution functions (RDFs), which can be found in the Supplementary material. The better agreement was found for the force fields due to Koller \textit{et al.} \cite{Koller_2012} and Batista \textit{et al.} \cite{Batista_2015}. Even though the model of Liu \textit{et al.} \cite{Liu_2014} presented small deviations, the simulation with rigid bodies qualitatively reproduced the RDFs obtained for flexible ions. Although not shown here, these conclusions are valid for other calculated RDFs: N(anion)-N(cation), C6(cation)-N(anion), C2(cation)-B(anion). The model of Weber and Kirchner \cite{Weber_2016}, 
on the other hand, presented important discrepancies in the RDFs of the pairs C5(cation)-N(anion) and C2(cation)-B(anion) when using rigid bodies. That is why, in this case only the imidazolium ring was considered rigid while the ethyl chain was left unconstrained.

@@

A study of dihedrals was also carried out for \ce{[emim][NTf_2]}. The CDF of dihedrals angles corresponding to torsions in C1-N2-C5-C6 and C2-N2-C5-C6, shown in Fig.~\ref{fig:die_ntf2}(a), resembles the behaviour of Fig.~\ref{fig:dihedrals_emim}(d), but the most likely angle of C1-N2-C5-C6 corresponds to 0$^{\circ}$. This similarity was expected as both models of \ce{[emim]^+} are based on the force field developed by Canongia-Lopes and P\'{a}dua~ \cite{Canongia_Lopes_2006}. With regards to the anion \ce{[NTf_2]^-}, Deetlefs \textit{et al.} \cite{Deetlefs_2006} have experimentally determined the conformer population of the liquid phase and observed that \ce{[NTf_2]^-} is mostly in its \textit{trans} conformation. Fig.~\ref{fig:die_ntf2}(b), which corresponds to the CDF for the contiguous C1-S1-N1-S2 and S1-N1-S2-C2, verifies qualitatively what was observed by Deetlefs \textit{et al.} \cite{Deetlefs_2006}. Given that the flexibility of \ce{[NTf_2]^-} gives rise to highly different conformation, a more rigorous strategy for building rigid bodies would be required. Thus, for \ce{[emim][NTf_2]} we have considered flexible ions and the DSF method, which resulted in a simulated density of 1.495 $\pm$ 0.009 g/cm$^3$ with an error of 1.12\% with respect to the experimental value~\cite{Tokuda_2005}.

@@

  \includegraphics[width=\linewidth]{Ludwig_anion.png}%
\caption{Combined distribution function (CDF) of anion}
\label{fig:die_ntf2}
\end{figure}

\begin{table*}
\begin{threeparttable}
\caption{Densities of \ce{[emim][B(CN)_4]} predicted from MD NPT simulations at 298.15 K and 1 atm. The experimental density is $\rho^{\text{exp}}$ = 1.036 g/cm$^{3}$~\cite{Doma_ska_2011}.}
\begin{tabular}{ c  c  c  c  c}  
\hline \hline
$\text{[emim]}$[B(CN)\textsubscript{4}] & $T_{\text{sim}}$ & $ P_{\text{sim}} $ & $\rho_{\text{sim}}$ & error (\%)\tnote{a} \\
model & (K) &  (atm) &  (g/cm$^{3}$) &  \\
			\hline
		 \multicolumn{5}{c}{Flexible ions/Ewald method}\\

Koller y col. \cite{Koller_2012}  & 298.14 $\pm$  0.02 & 0 $\pm$ 2 & 1.046 & 1.0 \\
Batista y col. \cite{Batista_2015} & 298.15 $\pm$ 0.01  & 1 $\pm$ 1 & 0.989 & 4.6  \\
Liu y col. \cite{Liu_2014}  & 298.14 $\pm$ 0.01 & 0 $\pm$ 1 & 1.001 & 3.4  \\
Weber y Kirchner. \cite{Weber_2016}  & 298.16  $\pm$ 0.01 & 1 $\pm$ 1 & 1.015 & 2.1  \\
	 \multicolumn{5}{c}{Rigid ions/DSF method}\\
Koller y col. \cite{Koller_2012}   & 298.42  $\pm$ 0.03  & 1 $\pm$ 1 & 1.038 & 0.2 \\
Batista y col. \cite{Batista_2015} & 298.43 $\pm$ 0.02  & 0.9 $\pm$ 0.7  & 0.988 & 4.7  \\
Liu y col. \cite{Liu_2014}  & 298.46 $\pm$ 0.02 & 1.2  $\pm$ 0.8 & 0.991 &  4.4 \\
Weber y Kirchner \cite{Weber_2016} &  298.41 $\pm$ 0.03 & 1.1 $\pm$ 0.8 & 1.022 & 1.4  \\
 \hline \hline
\label{table:props_dsf} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$($\rho^{\text{exp}}$$ - $$\rho^{\text{sim}}$)/$\rho^{\text{exp}}$.
\end{tablenotes}
\end{threeparttable}
\end{table*}

@@

For each model of \ce{[emim][B(CN)_4]} described in Sec~\ref{sec:force_field_il}, in Table \ref{table:henry} we present the results of solvation free energies of \ce{CO_2} along with the Henry constants ($K_s$) obtained by means of Eq.~\ref{eq:henry_eq}, which we compare with the experimental value reported by Mahurin \textit{et al.} \cite{Mahurin_2010}. Table \ref{table:henry} also includes the results for [emim][Tf\textsubscript{2}N] and the experimental $K_s$ obtained by Finotello \textit{et al.} \cite{Finotello_2008}. The uncertainties in $K_s$ were calculated using standard error propagation.

\begin{table*}
\centering
\begin{adjustbox}{width=1\textwidth}
\begin{threeparttable}
\caption{Results of solvation free energies and Henry constants of \ce{CO_2} in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] at T = 298.15 K and P = 1 atm. The experimental Henry constants in \ce{[emim][B(CN)_4]} and [emim][Tf\textsubscript{2}N] correspond to 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010} and 39.0 $\pm$ 0.1 atm \cite{Finotello_2008}, respectively.}
\begin{tabular}{ c c c  c  c  c  c }  
\toprule
Model & $\tilde{\rho}_{\text{sim}}$ & $\Delta G_{\,\text{LJ}}$  & $\Delta G_{\,\text{Coul}}$  & $\Delta G_{\,\text{sim}}$ & $K_{s}$ & error (\%)\tnote{a}\\
& (mol/dm$^{3}$) & (kcal/mol) & (kcal/mol) &  (kcal/mol) & (atm)  &  \\
			\hline
			\multicolumn{4}{c}{\ce{[emim][B(CN)_4]}} & \multicolumn{2}{c}{\cellcolor{gray!25}$K_{s}^{\text{exp}}$ = 38.9 $\pm$ 0.03 atm~\cite{Mahurin_2010}}\\
			\hline
Koller \textit{et al.} \cite{Koller_2012} & 4.5925 & 0.45 $\pm$ 0.01 & -1.06 $\pm$ 0.02 & -0.61 $\pm$ 0.02 & 40 $\pm$ 1 & 2.8 \\
Batista \textit{et al.} \cite{Batista_2015} & 4.3700 & 0.378 $\pm$ 0.008 & -1.24 $\pm$ 0.01  & -0.86 $\pm$ 0.01 & 24.9 $\pm$ 0.5 & 38.9 \\
Liu \textit{et al.} \cite{Liu_2014} & 4.3815 & 0.226 $\pm$ 0.009 & -1.11 $\pm$ 0.01 & -0.88 $\pm$ 0.01 & 24.3 $\pm$ 0.5 & 37.6  \\
Weber y Kirchner \cite{Weber_2016} & 4.5221 & 0.478 $\pm$ 0.009 & -1.23 $\pm$ 0.02 & -0.75 $\pm$ 0.02 & 31 $\pm$ 1 & 20.3  \\
\hline
		\multicolumn{4}{c}{[emim][Tf\textsubscript{2}N]} & \multicolumn{2}{c}{ \cellcolor{gray!25} $K_{s}^{\text{exp}}$ = 39.0 $\pm$ 0.1 atm~\cite{Finotello_2008}}\\
		\hline
 K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} &3.8205 & 0.389 $\pm$ 0.005 & -0.901 $\pm$ 0.006& -0.512 $\pm$ 0.008 & 39.4 $\pm$ 0.5  & 0.97  \\
 \bottomrule
\label{table:henry} 
\end{tabular}
\begin{tablenotes}
\item[a] error = 100 $\times$ $\abs{(K_s^{\text{exp}} - K_s^{\text{sim}})/K_s^{\text{exp}}}$.
\end{tablenotes}
\end{threeparttable}
\end{adjustbox}
\end{table*}

First, it should be pointed out that the result of $\Delta G_{\text{sim}}$ obtained for the model of Liu \textit{et al.} \cite{Liu_2014} is statistically identical to the value reported by those authors \cite{Liu_2014_1}, who applied the BAR method \cite{Bennett_1976} to independent simulations in $\lambda_{\,\text{vdW}}$ and $\lambda_{\, \text{Coul}}$. Moreover, the $\Delta G_{\text{sim}}$ of [emim][Tf\textsubscript{2}N] is very close to the value obtained by Kerl \textit{et al.} \cite{Kerl__2017} ($-0.534$ kcal/mol, with no uncertainty reported) using the FEP method \cite{Zwanzig_1954}. These consistencies serve for validating the methodological approaches we employed in each case.

From Table \ref{table:henry} one can see that the model of Koller \textit{et al.} \cite{Koller_2012} best reproduces the experimental value of $K_s$. If we look at the $\Delta G_{\lambda_{\,\text{vdW}}}$ profiles in Fig.~\ref{fig:deltag} we observe that for the models of Batista \textit{et al.} \cite{Batista_2015} and Liu \textit{et al.}~\cite{Liu_2014}, the maximum of the profiles occurs at lower values of free energies, suggesting that those models underestimate the interatomic interactions, which explains the ``facility'' to insert a \ce{CO_2} molecule as well as their failure to reproduce the experimental densities.

\begin{figure}[]
\includegraphics[width=\linewidth]{free_energy_paper}
\caption{$\Delta G_{\lambda_{\,\text{vdW}}}$ profiles of \ce{[emim][B(CN)_4]}.}
\label{fig:deltag}
\end{figure}

The $\Delta G_{\, \text{sim}}$ values for the models of Koller \textit{et al.} \cite{Koller_2012} and K\"{o}ddermann \textit{et al.} \cite{K_ddermann_2007} suggest a more favorable solvation of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in [emim][Tf\textsubscript{2}N].

We have also obtained the spatial distribution functions (SDFs) \cite{Svishchev_1993} using the software packages TRAVIS~\cite{Brehm_2011} and VMD~\cite{HUMP96}. For that, we carried out MD NPT simulations of the systems \ce{CO_2}-\ce{[emim][B(CN)_4]} and \ce{CO_2}-[emim][Tf\textsubscript{2}N] with a solute molar fraction of 0.1. In Fig.~\ref{fig:sdf_ions} we show the SDFs of the ions around a molecule of \ce{CO_2}. The isovalues were determined visually so as to observe the first solvation shell. From Fig.~\ref{fig:ludwig_sdf}(b), which correspond to the ions \ce{[emim]^+} and \ce{[NTf_2]^-}, it can be seen that the region with a low probability of finding an ion is larger than for \ce{[emim][B(CN)_4]}. In Fig.~\ref{fig:anions} we have plotted together the SDFs corresponding to the anions and we note that the first solvation shell due to [B(CN)\textsubscript{4}]$^{-}$ occurs at a sligthly shorter distance than for \ce{[NTf_2]^-}, in accordance with the more favorable solvation suggested by the free energy results.

@@

The task of accurately predicting $\gamma^{\, \infty}$ is more challenging given that, according to Eq.~\ref{eq:gamma_inf}, one should be able to reproduce the solvation free energies in both the pure solute and the solvent. In Table~\ref{table:mu_solutos} we present the simulated densities and the solvation free energies  $(\Delta G^{0}_{\text{sim}})$ of the pure solutes, which we compare against the experimental data extracted from the work of Chang~\cite{Chang_2009}. It should be pointed out that we were unable to find the experimental $\Delta G^{0}_\text{exp}$ of cyclohexane. Note that only in the case of ethanol we have reproduced $\Delta G^{0}_\text{exp}$, while the relative error for the other solutes is around 10\%.

The results of $\gamma^{\, \infty}$ for the solutes in \ce{[emim][B(CN)_4]} are shown in Table~\ref{table:gamma}. For benzene and water, the predictions are very accurate, but they are a result of error compensations given the divergences verified in Table~\ref{table:mu_solutos}. This makes necessary to review the force fields of the solutes. From Table \ref{table:gamma} one can also note that the experimental $\gamma^{\, \infty}$ for hexane at the close temperatures of 298.15 K and 303 K considerably differ. It is therefore difficult to assess the reliability of the simulated results in this case.
